---
title: "Gandaki province ERA5 hourly data"
author: "Shirish Maharjan"
date: "2023-10-17"
output: html_document
---

# List all the municaplities in gandaki pradesh [Step 1] [DONE]
# Calculate climate extremes of that municipalities [Step 2] [DONE]
# Calculate slope and p value of that municpalitie [Step 3]

# Load libraries 
```{r}
library(dplyr)
library(readxl)
```


# Step 1: List all the municaplities in gandaki pradesh [Step 1]
```{r}
grid_palika_join <- read_excel("E:/GIIS/ERA5 Hourly Data/Data/Grid_Palika_Join(Third)/Gird_Palika_join.xlsx")

gandaki_pradesh <- grid_palika_join %>% 
  select(Province, GaPa_NaPa) %>% 
  filter(Province == "Gandaki")

gandaki_pradesh <- unique(gandaki_pradesh$GaPa_NaPa)

class(gandaki_pradesh) 

gandaki_pradesh <- as.data.frame(gandaki_pradesh)

write.csv(gandaki_pradesh, "E:/GIIS/ERA5 Hourly Data/Gandaki province/Data/Municipality list (first)/municipality_list.csv")

```

# Load tempMax data 
```{r}
tempMax_1950_2022_municipality <- read.csv("E:/GIIS/ERA5 Hourly Data/Data/Average_grid_data (Fourth)/Municipality/tempMax_1950_2022_municipality.csv")

tempMin_1950_2022_municipality <- read.csv("E:/GIIS/ERA5 Hourly Data/Data/Average_grid_data (Fourth)/Municipality/tempMin_1950_2022_municipality.csv")

precTot_1950_2022_municipality <-  read.csv("E:/GIIS/ERA5 Hourly Data/Data/Average_grid_data (Fourth)/Municipality/precTot_1950_2022_municipality.csv")

```

# Select Gandaki pradesh municipalty only 
```{r}
tempMax_1950_2022_gandaki_municipality <- tempMax_1950_2022_municipality %>% 
  select(year, month, day,
Besishahar,
Dordi,
Dudhpokhari,
Kwholasothar,
MadhyaNepal,
Marsyangdi,
Rainas,
Sundarbazar,
Anbukhaireni,
Bandipur,
Bhanu,
Bhimad,
Byas,
Devghat,
Ghiring,
Myagde,
Rhishing,
Shuklagandaki,
Aandhikhola,
Arjunchaupari,
Bhirkot,
Biruwa,
Chapakot,
Galyang,
Harinas,
Kaligandagi,
Phedikhola,
Putalibazar,
Waling,
Annapurna,
Machhapuchchhre,
Madi,
Pokhara.Lekhnath,
Rupa,
Chame,
Narphu,
Nashong,
Neshyang,
Barhagaun.Muktikhsetra,
Dalome,
Gharapjhong,
Lomanthang,
Thasang,
Beni,
Dhaulagiri,
Malika,
Mangala,
Raghuganga,
Dhorpatan.Hunting.Reserve,
Bihadi,
Jaljala,
Kushma,
Mahashila,
Modi,
Painyu,
Phalebas,
Badigad,
Baglung,
Bareng,
Dhorpatan,
Galkot,
Jaimuni,
Kanthekhola,
Nisikhola,
Taman.Khola,
Tara.Khola,
Aarughat,
Ajirkot,
Bhimsen,
Chum.Nubri,
Dharche,
Gandaki,
Gorkha,
Palungtar,
Sahid.Lakhan,
Siranchok,
Sulikot,
Chitawan.National.Park,
Binayee.Tribeni,
Bulingtar,
Bungdikali,
Devchuli,
Gaidakot,
Hupsekot,
Kawasoti,
Madhyabindu)





tempMin_1950_2022_gandaki_municipality <- tempMin_1950_2022_municipality %>% 
  select(year, month, day,
Besishahar,
Dordi,
Dudhpokhari,
Kwholasothar,
MadhyaNepal,
Marsyangdi,
Rainas,
Sundarbazar,
Anbukhaireni,
Bandipur,
Bhanu,
Bhimad,
Byas,
Devghat,
Ghiring,
Myagde,
Rhishing,
Shuklagandaki,
Aandhikhola,
Arjunchaupari,
Bhirkot,
Biruwa,
Chapakot,
Galyang,
Harinas,
Kaligandagi,
Phedikhola,
Putalibazar,
Waling,
Annapurna,
Machhapuchchhre,
Madi,
Pokhara.Lekhnath,
Rupa,
Chame,
Narphu,
Nashong,
Neshyang,
Barhagaun.Muktikhsetra,
Dalome,
Gharapjhong,
Lomanthang,
Thasang,
Beni,
Dhaulagiri,
Malika,
Mangala,
Raghuganga,
Dhorpatan.Hunting.Reserve,
Bihadi,
Jaljala,
Kushma,
Mahashila,
Modi,
Painyu,
Phalebas,
Badigad,
Baglung,
Bareng,
Dhorpatan,
Galkot,
Jaimuni,
Kanthekhola,
Nisikhola,
Taman.Khola,
Tara.Khola,
Aarughat,
Ajirkot,
Bhimsen,
Chum.Nubri,
Dharche,
Gandaki,
Gorkha,
Palungtar,
Sahid.Lakhan,
Siranchok,
Sulikot,
Chitawan.National.Park,
Binayee.Tribeni,
Bulingtar,
Bungdikali,
Devchuli,
Gaidakot,
Hupsekot,
Kawasoti,
Madhyabindu)




precTot_1950_2022_gandaki_municipality <- precTot_1950_2022_municipality %>% 
  select(year, month, day,
Besishahar,
Dordi,
Dudhpokhari,
Kwholasothar,
MadhyaNepal,
Marsyangdi,
Rainas,
Sundarbazar,
Anbukhaireni,
Bandipur,
Bhanu,
Bhimad,
Byas,
Devghat,
Ghiring,
Myagde,
Rhishing,
Shuklagandaki,
Aandhikhola,
Arjunchaupari,
Bhirkot,
Biruwa,
Chapakot,
Galyang,
Harinas,
Kaligandagi,
Phedikhola,
Putalibazar,
Waling,
Annapurna,
Machhapuchchhre,
Madi,
Pokhara.Lekhnath,
Rupa,
Chame,
Narphu,
Nashong,
Neshyang,
Barhagaun.Muktikhsetra,
Dalome,
Gharapjhong,
Lomanthang,
Thasang,
Beni,
Dhaulagiri,
Malika,
Mangala,
Raghuganga,
Dhorpatan.Hunting.Reserve,
Bihadi,
Jaljala,
Kushma,
Mahashila,
Modi,
Painyu,
Phalebas,
Badigad,
Baglung,
Bareng,
Dhorpatan,
Galkot,
Jaimuni,
Kanthekhola,
Nisikhola,
Taman.Khola,
Tara.Khola,
Aarughat,
Ajirkot,
Bhimsen,
Chum.Nubri,
Dharche,
Gandaki,
Gorkha,
Palungtar,
Sahid.Lakhan,
Siranchok,
Sulikot,
Chitawan.National.Park,
Binayee.Tribeni,
Bulingtar,
Bungdikali,
Devchuli,
Gaidakot,
Hupsekot,
Kawasoti,
Madhyabindu)
```




# Calculate climate extremes of that municipalities [Step 2]

# Load Libraries 

```{r}
library(tidyverse)
library(climdex.pcic.ncdf)
library(ncdf4)
library(raster)
library(reshape2)
library(plyr)
require(scales)
library(climdex.pcic)
library(Kendall)
#library(ncdf)
library(PCICt)
library(dplyr)
```


# List of dailekh municpalities 

```{r}
#setwd("E:/GIIS/ERA5 Hourly Data/Gandaki province/Data/Climate extreme output(second)")

# List of words
words <- c("Besishahar",
"Dordi",
"Dudhpokhari",
"Kwholasothar",
"MadhyaNepal",
"Marsyangdi",
"Rainas",
"Sundarbazar",
"Anbukhaireni",
"Bandipur",
"Bhanu",
"Bhimad",
"Byas",
"Devghat",
"Ghiring",
"Myagde",
"Rhishing",
"Shuklagandaki",
"Aandhikhola",
"Arjunchaupari",
"Bhirkot",
"Biruwa",
"Chapakot",
"Galyang",
"Harinas",
"Kaligandagi",
"Phedikhola",
"Putalibazar",
"Waling",
"Annapurna",
"Machhapuchchhre",
"Madi",
"Pokhara.Lekhnath",
"Rupa",
"Chame",
"Narphu",
"Nashong",
"Neshyang",
"Barhagaun.Muktikhsetra",
"Dalome",
"Gharapjhong",
"Lomanthang",
"Thasang",
"Beni",
"Dhaulagiri",
"Malika",
"Mangala",
"Raghuganga",
"Dhorpatan.Hunting.Reserve",
"Bihadi",
"Jaljala",
"Kushma",
"Mahashila",
"Modi",
"Painyu",
"Phalebas",
"Badigad",
"Baglung",
"Bareng",
"Dhorpatan",
"Galkot",
"Jaimuni",
"Kanthekhola",
"Nisikhola",
"Taman.Khola",
"Tara.Khola",
"Aarughat",
"Ajirkot",
"Bhimsen",
"Chum.Nubri",
"Dharche",
"Gandaki",
"Gorkha",
"Palungtar",
"Sahid.Lakhan",
"Siranchok",
"Sulikot",
"Chitawan.National.Park",
"Binayee.Tribeni",
"Bulingtar",
"Bungdikali",
"Devchuli",
"Gaidakot",
"Hupsekot",
"Kawasoti",
"Madhyabindu")

# Create a directory to save CSV files
if (!file.exists("output_csv")) {
  dir.create("output_csv")
}

# Loop through each word and generate code
for (word in words) {
  
  base.period.historic <- c(1991, 2020)
    
    # Arrange date accordingly. 
    
  data.sub <- tempMax_1950_2022_gandaki_municipality %>%
      mutate(date = as.Date(paste(year, month, day, sep = "-"),
                            "%Y-%m-%d")) 
    
  this.dates <- as.PCICt(as.POSIXct(data.sub$date, tz = "GMT"),
                           cal = "gregorian")
  
  climdex.input <- climdexInput.raw(tmax=tempMax_1950_2022_gandaki_municipality[[word]],
                                    tmin=tempMin_1950_2022_gandaki_municipality[[word]],
                                    prec = precTot_1950_2022_gandaki_municipality[[word]],
                                    tmax.dates = this.dates,
                                    tmin.dates = this.dates,
                                    prec.dates = this.dates,
                                    base.range = base.period.historic,
                                    n = 5,
                                    northern.hemisphere = TRUE,
                                    tavg = NULL, tavg.dates = NULL,
                                    quantiles = NULL,
                                    temp.qtiles = c(0.1, 0.9),
                                    prec.qtiles = c(0.95, 0.99),
                                    max.missing.days = c(annual = 40, monthly = 10),
                                    min.base.data.fraction.present = 0.1)

              # CALCULATE INDICES
              ## ANNUAL INDICES
              ice_days <- climdex.id(climdex.input)
              frost_days <- climdex.fd(climdex.input)
              cdd <- climdex.cdd(climdex.input)
              cwd <- climdex.cwd(climdex.input)
              r99p <- climdex.r99ptot(climdex.input)
              r95p <- climdex.r95ptot(climdex.input)
              wsdi <- climdex.wsdi(climdex.input)
              csdi <- climdex.csdi(climdex.input)
              sdii <- climdex.sdii(climdex.input)
              gsl <- climdex.gsl(climdex.input)
              r10mm <- climdex.r10mm(climdex.input)
              r20mm <- climdex.r20mm(climdex.input)
              prcptot <- climdex.prcptot(climdex.input)
              
              ## MONTHLY INDICES
              tx10p <- climdex.tx10p(climdex.input)
              tx90p <- climdex.tx90p(climdex.input)
              tn90p <- climdex.tn90p(climdex.input)
              txx <- climdex.txx(climdex.input)
              txn <- climdex.txn(climdex.input)
              tnn <- climdex.tnn(climdex.input)
              tnx <- climdex.tnx(climdex.input)
              dtr <- climdex.dtr(climdex.input)
              rx1day <- climdex.rx1day(climdex.input)
              rx5day <- climdex.rx5day(climdex.input)

  ## MERGE INDICES
  annual.indices <- data.frame(cbind(ice_days, frost_days, cdd, cwd, r99p,
                                     r95p, wsdi, csdi, sdii, gsl, r10mm, r20mm,
                                     prcptot)) %>% 
    mutate(Municipality = word)

  monthly.indices <- data.frame(cbind(tx10p, tx90p, tn90p, txx,
                                      txn, tnn, tnx, dtr, rx1day, rx5day)) %>% 
    mutate(Municipality = word)
  
  # Save the results as CSV files with word's name in the file
  write.csv(annual.indices, file = paste0("output_csv/", word, "_annual_indices.csv"))
  write.csv(monthly.indices, file = paste0("output_csv/", word, "_monthly_indices.csv"))
}
```


# Merge Annual Indices and Monthly indices all together in dailkeh and sarlahi 

```{r}

# Set the working directory to the folder containing the CSV files.
setwd("E:/GIIS/ERA5 Hourly Data/Gandaki province/Data/Climate extreme output(second)")

# Get a list of all the CSV files in the working directory.
csv_files <- list.files(pattern = "*_annual_indices.csv")

# Read all the CSV files into a list of data frames.
data_frames <- lapply(csv_files, read.csv)

# Merge all the data frames in the list into a single data frame.
merged_data_frame <- bind_rows(data_frames)

# Save the merged data frame to a new CSV file.
write.csv(merged_data_frame, "ANNUAL_MERGED_DATA.csv")

```


# Calculate slope and p value of that municpalitie [Step 3]

```{r}

gandaki_annual_indices <- read.csv("E:/GIIS/ERA5 Hourly Data/Gandaki province/Data/Climate extreme output(second)/ANNUAL_MERGED_DATA.csv")

gandaki_monthly_indices <- read.csv("E:/GIIS/ERA5 Hourly Data/Gandaki province/Data/Climate extreme output(second)/MONTHLY_MERGED_DATA.csv")

# Load the required packages
library(trend)
library(Kendall)

# ANNUAL INDICES

# Create an empty data frame to store the results
results <- data.frame(Municipality = character(0), Index = character(0), Sensitivity_Slope = numeric(0), MK_P_Value = numeric(0))

# List of climate indices
climate_indices <- c(
  "ice_days", "frost_days", "cdd", "cwd", "r99p", "r95p",
  "wsdi", "csdi", "sdii", "gsl", "r10mm", "r20mm", "prcptot"
)

# Split the data frame by Municipality
municipality_groups <- split(gandaki_annual_indices, gandaki_annual_indices$Municipality)

# Loop through each municipality group
for (municipality in names(municipality_groups)) {
  municipality_data <- municipality_groups[[municipality]]
  
  # Loop through each climate index
  for (index_name in climate_indices) {
    # Extract the column data
    ci_values <- municipality_data[[index_name]]
    
    # Calculate the sensitivity slope
    sens_slope_result <- sens.slope(ci_values)
    
    # Calculate the Mann-Kendall p-value
    mk_test_result <- mk.test(ci_values)
    
    # Store the results in the 'results' data frame
    results <- rbind(results, data.frame(Municipality = municipality, Index = index_name, Sensitivity_Slope = sens_slope_result$estimates, MK_P_Value = mk_test_result$p.value))
  }
}

# Print the results
write.csv(results,  "E:/GIIS/ERA5 Hourly Data/Gandaki province/Data/Sens slope and p value(third)/gandaki_annual_slope_p.csv", row.names = FALSE)



# MONTHLY INDICES

# Create an empty data frame to store the results
results <- data.frame(Municipality = character(0), Index = character(0), Sensitivity_Slope = numeric(0), MK_P_Value = numeric(0))

# List of climate indices
climate_indices <- c(
  "tx10p","tx90p","tn90p","txx","txn","tnn","tnx","dtr","rx1day","rx5day")

# Split the data frame by Municipality
municipality_groups <- split(gandaki_monthly_indices, gandaki_monthly_indices$Municipality)

# Loop through each municipality group
for (municipality in names(municipality_groups)) {
  municipality_data <- municipality_groups[[municipality]]
  
  # Loop through each climate index
  for (index_name in climate_indices) {
    # Extract the column data
    ci_values <- municipality_data[[index_name]]
    
    # Calculate the sensitivity slope
    sens_slope_result <- sens.slope(ci_values)
    
    # Calculate the Mann-Kendall p-value
    mk_test_result <- mk.test(ci_values)
    
    # Store the results in the 'results' data frame
    results <- rbind(results, data.frame(Municipality = municipality, Index = index_name, Sensitivity_Slope = sens_slope_result$estimates, MK_P_Value = mk_test_result$p.value))
  }
}

# Print the results
write.csv(results,  "E:/GIIS/ERA5 Hourly Data/Gandaki province/Data/Sens slope and p value(third)/gandaki_monthly_slope_p.csv", row.names = FALSE)



```


